Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-12 rnni_convexity.tex
nope proof has holes two...

\begin{proof}
Let $T$ and $R$ be trees as defined in the lemma.
Notice that the only $\rnni$ move on $T$ that could decrease the rank of $\mrca_T(C_k)$ are $\nni$ moves on the edge between $\mrca_T(C_k)$ and its child (if this edge has length one), or a rank move between $\mrca_T(C_k)$ and the node with rank one less.
Therefore, we will now distinguish these two cases:
Either there is an edge $(v,w)$ between nodes $v = \mrca_T(C_k)$ and $w$ with rank $rank_T(w) = rank_T(v) - 1$, or there is no such edge.

@@

Note that the uniqueness of the $\rnni$ move in Line~\ref{alg:findpath:line:move_set_down} of the algorithm $\findpath$ also implies that the algorithm is deterministic.
The running time of the algorithm is quadratic in the number of taxa.

Because the algorithm returns a path between pairs of trees in $\rnni$, the length of the path approximates the $\rnni$ distance from above.
A natural question then is how accurate this approximation is.
We have computationally shown that the algorithm $\findpath$ finds the correct distance for trees up to six taxa.
Specifically, we have implemented $\findpath$ \autocite{Collienne2019} and compared the results with the true $\rnni$ distance as explained earlier in this section.

>>>>

\todo{We never use $R$ in this proof, so $B_k$'s are irrelevant in Lemma.}
\begin{proof}
Let $T$ and $R$ be trees as defined in the lemma.
Notice that the only $\rnni$ move on $T$ that could decrease the rank of $\mrca_T(C_k)$ are $\nni$ moves on the edge between $\mrca_T(C_k)$ and its child (if this edge has length one), or a rank move between $\mrca_T(C_k)$ and the node with rank one less.
Therefore, we will now distinguish these two cases:
Either there is an edge $(v,w)$ between nodes $v = \mrca_T(C_k)$ and $w$ with rank $rank_T(w) = rank_T(v) - 1$, or there is no such edge.

@@

Clearly, the worst-case complexity of $\findpath$ is quadratic in the number of taxa.

Because the algorithm returns a path between pairs of trees in $\rnni$, the length of the path approximates the $\rnni$ distance from above.
A natural question then is how accurate this approximation is.
We have computationally shown that the algorithm $\findpath$ finds the correct distance for trees up to seven taxa \autocite{Collienne2019}.
